A Multi-Modal Model for Prediction and Classification of Object Deformation during Robotic Manipulation

### 2016-08-25 twostagedo.tex

\subsection{Integration Scheme}
\label{sec:ischeme}
Rather than using the traditional Newton equations with a numeric integration scheme like Euler of Verlet, we made the velocities proportional to the forces:
\begin{equation}
 \vec{x}(t+h) = \vec{x}(t) + h \dfrac{\vec{F(t)}}{m}\label{eq:integration}
\end{equation}
with $\vec{F}(t) = \vec{F}_D(t) + \vec{F}_A(t) + F_\varphi(t)$ being the sum of the forces for the preservation of length, area and angle respectively and $\vec{x}(t+h)$, the position of the vertex at time $t+h$.  The simulations obtained were closer to the observed behaviour, because there is not inertia in the oscillation.
When experimenting with different integration steps, force values were interpolated between measuremente.

\subsection{Collision Detection}
In the scenario, rigid objects are treated as geometric obstacles.  Two types of obstacles are considered: circles and a floor line that can not be crossed.  For the floor obstacle, the collision is roughly solved by pushing vertices back to the border of the floor.  The springs will eventually propagate the effect to the neighbours.  For the circle the resolution is in two stages: vertices and edges.  A vertex will be pushed out to a distance $\epsilon$ of the finger, in the direction of the radius.  For edges, the common algorithm in \alref{alg:point_segment} is used to estimate the shortest distance between the centre of the circle and the edge.  Given this distance, the algorithm in \alref{alg:push_edge} indicates how and in which direction the edge must be displaced.

>>>>

\subsection{Integration Scheme}
\label{sec:ischeme}
Rather than using the traditional Newton equations with a numeric integration scheme like Euler \comment{or} Verlet, \comment{used twice to solve the second order differential equiations,} we made the \comment{\sout{velocities proportional to the forces:} force proportional to the velocity:
\begin{align}
 F(t) = m \dfrac{\partial \vec{p}}{\partial t}
\end{align}
and applied Euler only once to solve for $p$:
\begin{equation}
 \vec{p}(t+h) = \vec{p}(t) + h \dfrac{\vec{F(t)}}{m}\label{eq:integration}
\end{equation}}
with $\vec{F}(t) = \vec{F}_D(t) + \vec{F}_A(t) + F_\varphi(t)$ being the sum of the forces for the preservation of length, area and angle respectively and $\vec{p}(t+h)$, the position of the vertex at time $t+h$.  \comment{We acknowledge that this is not the proper Newtonian model, however t}he simulations obtained were closer to the observed behaviour, because there is not inertia in the oscillation.
When experimenting with different integration steps, force values were interpolated between measurements.

\subsection{Collision Detection}
In the scenario, rigid objects \comment{(like the robotic finger and the table)} are treated as geometric obstacles.  \comment{When the simulation of the behaviour of the mesh, that models the image of the sponge, is carried on, the predicted positions of the vertices may indicate that the mesh penetrates the obstacles.  This should be interpreted as a collision between the sponge and the obstacle.  Since the sponge can not penetrate an obstacle, the overlapping between geometries must be solved, and its physical consequences must affect the simulation.  For example: if vertices of the mesh overlap the table, the sponge will remain on top of the table, with its material being more compact, which will cause the response force propagated towards the finger to be increased.

In order to model this,} two types of \comment{solid} obstacles are considered: circles \comment{(for the finger)} and a table line that can not be crossed.  For the table obstacle, the collision \comment{of parts of the sponge with it} is roughly solved by pushing vertices \comment{of the mesh of the sponge} back to the border of the table.  The springs will eventually propagate the effect to the neighbours.  For the circle the resolution is in two stages: vertices and edges.  A vertex will be pushed out to a distance $\epsilon$ of the finger, in the direction of the radius.  For edges, the common algorithm in \alref{alg:point_segment} is used to estimate the shortest distance between the centre of the circle and the edge.  Given this distance, the algorithm in \alref{alg:push_edge} indicates how and in which direction the edge must be displaced.
